\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/badusb.tex
change of caption order
fix
more, not done.

Figure~\ref{fig:attack_model} shows the architecture of our attack model. \mycircled{1} represents the victim's devices; \mycircled{2} is our \tool; \mycircled{3} is the attacker's remote PC. The details of each component in \tool are as follows.\mycircled{1}

@@

\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by embedded computer.
	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted via GSM/WiFi to the attacker.
	\item\textit{HID Emulator} emulates HID device which can be controlled from the attacker.
\end{itemize}

>>>>

Figure~\ref{fig:attack_model} shows the architecture of our attack model. \mycircled{1} represents the victim's devices; \mycircled{2} is our \tool; \mycircled{3} is the attacker's remote PC. The details of each component in \tool are as follows.

@@

\begin{itemize}

	\item\underline{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port, etc.

	\item\underline{Video Capture Card} converts DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by the Single Board Computer (i.e., an embedded computer).

	\item\underline{HID Emulator} emulates HID device which can be controlled from the attacker.

	\item\underline{Single Board Computer} processes video stream from the victim via the Video Capture Card or sends commands to the victim via HID Emulator.

	\item\underline{Wi-Fi/GSM Module} transmits the sensitive data or receives commands to/from the remote attacker PC.

\end{itemize}
